### 2024-06-02 2024-5-13/sections/conclusion.tex
the expriments finished
experiments on NestC benchmark suite

This work proposed an efficient automata-theoretical approach for solving string constraints with regex-counting and string-length. The approach is based on encoding counting operators in regular expressions by cost registers symbolically instead of unfolding them explicitly. Moreover, this work proposed automata-size reduction techniques to improve performance further. Finally, we used two benchmark suites comprising 48,843 instances in total to evaluate the performance of our approach. The experimental results show that our approach can solve more instances than the state-of-the-art best solvers, at a comparable or faster speed, especially when the counting and length bounds are large. 
For the future work, we plan to investigate how the symbolic approach can be extended to reason about nested counting operators.

>>>>

This work proposed an efficient automata-theoretical approach for solving string constraints with regex-counting and string-length. The approach is based on encoding counting operators in regular expressions by cost registers symbolically instead of unfolding them explicitly. Moreover, this work proposed various optimization techniques to improve the performance further. Finally, we used three benchmark suites comprising 49,843 instances in total to evaluate the performance of our approach. The experimental results show that our approach can solve more instances than the state-of-the-art best solvers, at a comparable or faster speed, especially when the counting and length bounds are large or when counting operators are nested with some other counting operators or complement operators. 
%For the future work, we plan to investigate how the symbolic approach can be extended to reason about nested counting operators.

### 2024-06-02 2024-5-13/sections/implementation.tex
NestC benchmark suite
add results of the NestC benchmark suite
experiments on NestC benchmark suite

For the benchmarks that contain the nestings of counting operators and a complement operator, we utilize the following template
\[x \in e_{comp1} \wedge x \in e_{comp2} \wedge x \in e_{sani} \wedge |x| > 50, \]
where both $e_{comp1}$ and $e_{comp2}$ are of the form $\overline{e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}} e_4^{\{m_4, n_4\}}}$, such that for each $i \in [4]$, $20 \leq m_i\leq n_i\leq 1000$  and $e_i$ contains no counting operators. Note that two regular expressions $e_{comp1} $ and $e_{comp2}$ are introduced to have a better balance between the numbers of satisfiable and unsatisfiable instances.

@@

\begin{table}[htbp]
  \centering\vskip 0pt
    \import{tables}{table_regcol.tex}
    \caption{Overall performance evaluation}
  \label{tab:table_overall_eval}
\end{table}
%To answer \textbf{Q1}, \textbf{$\ostrichrecl$ is the second fastest solver on these benchmark suites, and it solves the most number of instances}.

>>>>

For the benchmarks that contain the nestings of counting operators and a complement operator, we utilize the following template
\[x \in e_{comp1} \wedge x \in e_{comp2} \wedge x \in e_{sani} \wedge |x| > 50, \]
where both $e_{comp1}$ and $e_{comp2}$ are of the form $\overline{e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}} e_4^{\{m_4, n_4\}}}$, such that for each $i \in [4]$, $20 \leq m_i\leq n_i\leq 1000$  and $e_i$ contains no counting operators. Note that two regular expressions $e_{comp1} $ and $e_{comp2}$ are introduced to have a better balance between the numbers of satisfiable and unsatisfiable instances. Based on this template, we also generate 500 instances.

In total, the NestC benchmark suite contains 1000 instances.

@@

\begin{table}[htbp]
  \centering\vskip 0pt
    \import{tables}{table_regcol.tex}
    \caption{Overall performance evaluation}
  \label{tab:table_overall_eval}
\end{table}

Furthermore, in order to see how $\ostrichrecl$ performs on the RECL constraints where the counting and length bounds are large or when the counting operators are nested with some other counting operators or with complement operators, we also compare $\ostrichrecl$ with the other solvers solely on the NestC benchmark suite. The experiment results can be found in Table~\ref{tab:table_nestc_eval}. From the results, we can see that $\ostrichrecl$ outperforms the other solvers in both the number of solved instances and the average time. Specifically, $\ostrichrecl$ solves 873 out of 1000 instances, while the best state-of-the-art solver (Z3seq) solves only 518 instances.  Moreover, while the average time of $\ostrichrecl$  is only slightly better than Z3str3RE (19.49s versus 20.09s), $\ostrichrecl$ solves much more instances than it (873 versus 170). The results show the great advantage of $\ostrichrecl$ against the other solvers on the NestC benchmark suite.

\begin{table}[htbp]
  \centering\vskip 0pt
    \import{tables}{table_nestc.tex}
    \caption{Performance evaluation on the NestC benchmark suite}
  \label{tab:table_nestc_eval}
\end{table}
%To answer \textbf{Q1}, \textbf{$\ostrichrecl$ is the second fastest solver on these benchmark suites, and it solves the most number of instances}.
